### 2017-11-06 Draft2/AsymptoticNotation.tex
More stuff for today

\subsection{Motivation}

In order to highlight the benefit of growth arrays, I will use an alternative notation for time complexity. The reason for this is, for certain operations, growth arrays are only better than dynamic arrays by a constant factor. For example, dynamic arrays might allocate roughly $2n$ memory for appending $n$ items, while growth arrays would allocate roughly $n$ memory. Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(n)$.

My goal is to be able to compare the coefficients of the highest-order terms in both expressions. For example, I would like to take the ratio $\frac{2n}{n}$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$. However, big-O notation does not support this.

\subsection{Definition}

To analyze time complexity, I will use the $\sim$ relation. It is defined as follows:

\begin{align*}
f \sim g \leftrightarrow \lim_{n \to \infty} \frac{g}{f} = 1
\end{align*}

This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

\subsection{Properties}
\label{subsec:AsymptoticProperties}

>>>>

\subsection{Introduction}

Typically, big-O notation is used to analyze the time or space complexity of a function. In order to highlight the benefit of growth arrays, however, I will use the $\sim$ relation to analyze complexity. This is because for certain operations, growth arrays are only better than dynamic arrays by a constant factor. For example, dynamic arrays might use roughly $2n$ space for appending $n$ items, while growth arrays would use roughly $n$ space. Even though growth arrays are clearly better in this regard, the big-O space complexity for both data structures would be the same, $O(n)$.

My goal is to be able to compare the coefficients of the highest-order terms in both expressions. For example, I would like to take the ratio $2n / n$, see that it is $2$, and conclude that dynamic arrays allocate roughly twice as much as growth arrays for large $n$. However, big-O notation does not support this.

\subsection{Definitions}

I will mainly use the $\sim$ relation to analyze complexity. It is defined as follows:
\begin{align*}
f \sim g \leftrightarrow \lim_{n \to \infty} \frac f g = 1
\end{align*}
This is read as "$f$ is asymptotic to $g$" or "$f$ and $g$ are asymptotic." {\HdrNote} $f$ and $g$ are used as shorthand to denote $f(n)$ and $g(n)$, respectively.

@@

I will also introduce the cousins of $\sim$, $\FluteLess$ and $\FluteLeq$. $f \FluteLeq g$ if and only if $f \FluteLess g$ or $f \sim g$. $\FluteLess$ is defined as follows:
\begin{align*}
f \FluteLess g \leftrightarrow \lim_{n \to \infty} \frac f g < 1
\end{align*}
\subsection{Properties}
\label{subsec:AsymptoticProperties}
